---
title: "Risk based evaluations of competing agronomic climate adaptation strategies: Workflow example for Bihar"
format: html
fig-dpi: 300
fig-width: 8.88
fig-align: center
fig-height: 5

self-contained: true
author: Maxwell Mkondiwa and Anton Urfels
editor: visual
toc: true
toc-location: left
number-sections: true
execute: 
  message: false
  warning: false
  echo: true
---

# Introduction

# Stylized example

```{r}

# Hypothetical Comparisons ---------------------------------------------------

# Theoretical graphs ------------------------------------------------------------

# Truncated normal -----------------------
library(truncnorm)

seed(232)

g <- rtruncnorm (n=1000,a=4,b=8, mean=6,sd=0.8 )
q <- rtruncnorm (n=1000,a=4,b=8, mean=5,sd=1 )
f <- rtruncnorm (n=1000,a=3,b=9, mean=5,sd=2 )
df <- data.frame(x = c(g, q, f),Scenarios = factor(rep(c("G","Q","F"), c(1000,1000,1000))))
df <- df[order(df$x), ]

df$ecdf <- ave(df$x, df$Scenarios, FUN=function(x) seq_along(x)/length(x))

library(ggplot2)
stochasticdominance=ggplot(df, aes(x, ecdf, colour =   Scenarios,linetype=Scenarios)) + 
  geom_line(lwd=c(1.5))+
  scale_linetype_manual(values = c(1,2,3))+
  # theme(axis.ticks = element_blank(),axis.text.x = element_blank()) +
  xlab("Yield (tons/ha)") +
  ylab("Cumulative probability") +
  scale_color_manual(values = c("grey","black","black"))+
  theme(panel.grid.major.x = element_blank())+
  theme(panel.grid.minor.x = element_blank())
previous_theme <- theme_set(theme_bw())
stochasticdominance

ggsave("Hypothetical/Figure_stochasticdominance_truncated_normal.png",dpi=300)

```

## Export data for comparisons in Octave

```{r}
# Data for stochastic dominance comparisons ------------------------------------
ID=rep(1,1000)
g=as.data.frame(g*1000)
q=as.data.frame(q*1000)
f=as.data.frame(f*1000)
Rep=1:nrow(g)
Area=rep(1,1000)


QvsG=data.frame(ID,Rep,Area,q,g)
export(QvsG,colNames=F,"Hypothetical/QvsG.xlsx")

QvsF=data.frame(ID,Rep,Area,q,f)
export(QvsF,colNames=F,"Hypothetical/QvsF.xlsx")

FvsG=data.frame(ID,Rep,Area,f,g)
export(FvsG,colNames=F,"Hypothetical/FvsG.xlsx")

# Experiments -------------

# G vs Q: Q as baseline -----------------
GvsQ=data.frame(ID,Rep,Area,g,q)
export(GvsQ,colNames=F,"Hypothetical/GvsQ.xlsx")


## F vs Q: Q as baseline ---------------
FvsQ=data.frame(ID,Rep,Area,f,q)
export(FvsQ,colNames=F,"Hypothetical/FvsQ.xlsx")

## G vs F: F as baseline ----------------
GvsF=data.frame(ID,Rep,Area,g,f)
export(GvsF,colNames=F,"Hypothetical/GvsF.xlsx")


```

## Octave model

```{Matlab}
pkg install io-2.6.4.tar.gz
pkg load io


% 1 Q as baseline vs G ---------------------------------------------
clear
ndataseq01060216=xlsread('GvsQ.xlsx')
CreateWTPBoundsbyCell
CreateTableData


xlswrite('RA_GvsQ',RA)
xlswrite('DescriptiveStat_GvsQ_.xlsx',DescriptiveStat)






```

# Bihar Model Application

# Conclusion

# References 

Hurley, T., Koo, J., & Tesfaye, K. (2018). Weather risk: how does it change the yield benefits of 395 nitrogen fertilizer and improved maize varieties in sub-Saharan Africa? Agricultural 396 Economics, 49(6), 711-723. https://doi.org/https://doi.org/10.1111/agec.12454.

Mkondiwa, M., and Urfels, A. 2023. "Risk-based evaluations of competing agronomic climate adaptation strategies: The case of rice planting strategies in the Indo Gangetic Plains". Working Paper.
